### 2019-02-13 sections/intuition.tex
add higher order example: twice

\fixme{Add example about higher order tasks}

>>>>

\begin{example}[Twice]

A simple higher-order task which performs a task twice can be specified as follows.
\begin{TASK}
  let twice : Task $\tau$ -> Task $\tau$ = \t : Task $\tau$.
    t >>? \x : $\tau$. t
\end{TASK}
By using the step combinator $\When$ we specify that the given task \TS{t} should be performed a second time.
The result \TS{x} from the first run is ignored.
